---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Rmessy

<!-- badges: start -->
<!-- badges: end -->

The goal of Rmessy is to Help lazy analysts to save some effort and time.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("asitav-sen/Rmessy")
```

## Functions

### juggling_jaguar

This takes a data frame, creates data frames by selecting combination of two columns then binds them together in rows.

#### Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Rmessy)
a<-c("A","a")
b<-c("B","b")
c<-c("C","c")
d<-c("D","d")

df<-data.frame(a,b,c,d)

Rmessy::juggling_jaguar(df)



```
The function is useful to build files for network analysis which takes relationship values in two columns. However, in real life, data usually don't come in that way. Read the 'Vignette' for further clarity.

### mapping_monkey

This takes an igraph file and calculates degree, betweenness, eigen_centrality, edge_density, diameter, farthest_vertices, get_diameter, assortativity.degree and transitivity. Finally, returning a list with the results.

#### Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}


Rmessy::mapping_monkey(graphitem, mode="all",norm=TRUE, direc=FALSE, loops=FALSE)


```

### bestmccplot

Plots Matthews Correlation Coefficient (MCC) against cutoff values.


```{r}
Rmessy::bestmccplot(c(1,0,1,0,1,1,0,0), c(0.2, 0.3, 0.4, 0.5, 0.6, 0.9, 0.3, 0.8))
```

### bestmcc

Returns the highest MCC among the all the MCCs calculated at cutoffs between 1% to 100% in sequence of 1%

```{r}
Rmessy::bestmcc(c(1,0,1,0,1,1,0,0), c(0.2, 0.3, 0.4, 0.5, 0.6, 0.9, 0.3, 0.8))
```

### Set of modules

A set of modules for use with Shiny apps. These cannot be run without shiny. Kindly go through the introduction file to go through the list.
You can see them in action as this shiny [dashboard for predictive](https://asitav-sen.shinyapps.io/nitirun/).

